Post CMOS technologies: An Overview and Analysis

### 2025-05-28 Paper.tex
memristors

\section{Memristors}

>>>>

\section{Memristors}
The Von Neumann architecture, which physically separates the processing 
unit from the memory has been the preferred method for making computers. 
However, as our chips become faster bottlenecks from I/O also come up 
where information can't be moved to and from the chip fast enough. Memristors, 
first described as the fourth missing circuit element, offer a way 
to link memory and compute in a single device. This combination opens up
potential for more efficient brain inspired computing, particularly 
in the neuromorphic and analog world.

\subsection{The Memristor Concept}
A memristor, combination of the words memory and resistor, is a device 
that can have a programmble resistance. It was often described as 
the fourth circuit element because it was believed that magnetic fields 
could be used to change the resistance of these devices. However, recent 
devices don't rely on magnetic fields at all and instead use electric fields 
to change the physical and chemical properties of these devices to program 
the resistance. This property, where it can "remember" its resistance allows 
for non volatile memory and reconfigurable logic without having to change 
the physical connections on a chip.

In addition to these new computing regimes they also offer advantages 
in several other areas. They can be manufactured into nanoscale 
dimensions below those of a silicon transistor allowing for greater scaling 
and higher density integration. Their ability to store memory even 
when power is switched enables lower power consumption. Since they can 
also be programmed into continuous resistance values they have the 
ability to store more than just 1 bit per device. Recent experiments
have shown one memristor being able to store 5-7 bits. Advances 
in memristors have also demonstrated a high level of CMOS compatability 
allowing them to be used in hybrid structures with traditional CMOS 
devices.

\subsection{Memristor Based Threshold Logic Gate (TLG)}
Beyond their abilities to store memory, memristors are perfectly suited 
for implementing threshold logic gates.
